Review of Assigned Readings

### 2018-01-03 paper/paper.tex
improving the text for 2.3 data collection

\subsection{Data Collection}
For our dataset, we used 2 different sources.\\
We first collected historical data on bitcoin prices to USD and secondly, we gathered twitter massages related to bitcoin. We fulfil this relationship by selecting tweets that contain the term “bitcoin” in the text message. The time period for both collected data sets was from 19.12.2017 20:00:00 UTC to 28.12.2017 10:00:00 in an hourly basis. We chose an hourly basis to be able to do a statistical analysis with a certain amount of observation for the restricted processing time of this homework.\\

@@

For the bitcoin prices, a publicly available API from CoinDesk was used (Source? See documentation?). The prices collected represent the final price level of bitcoin before every hour changes. For example, our first listed price of bitcoin was on 19.12.2017 at 19:59:59 and our last value on 28.12.2017 at 09:59:59. These values construct our first time series data set and are shown in the following graph.\\

>>>>

\subsection{Data Collection}
For our data, we collected 2 separated time series datasets. One showing the twitter activity regarding bitcoin and the second one showing the bitcoin price development. Both datasets, were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC. We chose the hourly basis to be able to do a statistical analysis with a certain amount of observations in the restricted processing time for this homework. For the twitter data we aggregated every hour the total number of tweets mentioning bitcoin. For the bitcoin prices we selected prices at the last second of every hour.\\
The following figure displays the twitter activity regarding bitcoin for the observed time period. The first plot shows the hourly change of the aggregate number of tweets containing bitcoin. In the second and third plots we did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis. The graphs show overall a cyclical movement arount 1200 tweets and a single outburst on the 22.12.2017 for the time interval between 15:00:01 and 21:00:00 with highest value being 4622 tweets in one hour.\\

@@

Next we display the time series data on bitcoin price development for the observed time period. The first plot shows the hourly changes of bitcoin prices. The second and third plots are once again first difference transormations of the main variable for the later analysis. In this graph we observe a notably volatile movement and no spesific direction. This contradicts the recent trend of rising bitcoin prices in the months, but that happens because we observe a small period of a week in which bitcoin happened to have a neutral price development.\\
